---
title: "hybridogram"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hybridogram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package takes a list of hybridization experiment results in a 
simple text file:

| species 1 | species 2 | code |
|----------:|:---------:|:-----|
| Phoca largha | Phoca vitulina | 1 |
| Phoca largha | Phoca caspica | 2 |
| Phoca caspica | Pusa hispida | 2 |

---

Another text file contains code for the different hybridization result types:

| code | description |
|-----:|:------------|
| 1 | No hybrid |
| 2 | Documented hybrid |
| 3 | Hybrid with same 3rd species |

---

Call the hybridogram function:
```{r eval=FALSE}
library(hybridogram)

V1 <- c("Phoca largha","Phoca largha","Phoca caspica")
V2 <- c("Phoca vitulina","Phoca caspica","Pusa hispida")
V3 <- c(2,3,3)
hybrid_data <- data.frame(V1,V2,V3)
C1 <- c(1,2,3)
C2 <- c("No hybrid","Documented hybrid","Hybrid with same 3rd species")
codes <- data.frame(C1,C2)
hybridogram(hybrid_data, codes)
```

This will produce a heat map, which is the hybridogram. It is a square and
symmetric heat map showing the hybrid relationships between all pairs of species.
A color legend in the lower right corner shows what color each code is represented by.
